Arc Blanc: a real time ocean simulation framework

### 2025-01-10 paper.tex
Clarify section about relation of dispersion in appendix

Note that while the third equation of system \ref{equa:systemTessendorf} is not used here, it can help to deduce the \emph{dispersion relation}.

>>>>

The third equation of the system \ref{equa:systemTessendorf} gives the following equality:
\begin{equation}
\label{equa:derivHeqDerivPhi}
\frac{\partial h}{\partial t}(\mathbf{k},t)=\frac{\partial\phi}{\partial y}(\mathbf{k}, 0, t)
\end{equation}
Once again, we only considered one wave vector $\mathbf{k}$ as Equations are all linear, in consequence Equation \ref{equa:derivHeqDerivPhi} becomes:

\begin{align}
\frac{\partial \tilde{h}}{\partial t}(\mathbf{k},t) - \frac{\tilde{\partial}\phi}{\partial y}(\mathbf{k}, 0, t) &=0 \nonumber\\
i\omega(k)\left(\tilde{h}_0(\mathbf{k})\exp(i\omega(k)t)-\tilde{h}_0^*(-\mathbf{k})\exp(-i\omega(k)t)\right) - \frac{igk}{\omega(k)} E(\mathbf{k},0)\nonumber\\
 \times \left(\tilde{h}_0(\mathbf{k})\exp(i\omega(k)t)-\tilde{h}_0^*(-\mathbf{k})\exp(-i\omega(k)t)\right) &= 0 \nonumber\\
 \omega(k)- \frac{gk}{\omega(k)} &= 0 \nonumber\\
 \omega(k) = \sqrt{gk} \label{equa:relationDispersionDeduce}
\end{align}

This last Equation \ref{equa:relationDispersionDeduce} gives the expression of the dispersion relation used in the Section \ref{sec:oceanWaves}.
